Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-07 HGmodelMANUSCRIPT/coverLETTER.tex
Update coverLETTER.tex

Please find attached to this message a manuscript that we would like to submit for publication 
in \textit{Journal of the american chemical society} (JACS): 
`Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions', 
by A. Botan et al. In the manuscript we combine extensive amount of experimental Nuclear Magnetic Resonance (NMR)
and molecular dynamics simulation data to understand the atomistic resolution structure of biologically abundant phospholipid molecules.

We believe that the manuscript is interesting for the wide and diverse contemporary audience of
JACS since the used combination of experiments and simulations is shown to be successfull in
resolving the atomistic resolution structure of biomolecules in the various biologically relevant conditions.
The approach is demonstrated for lipids, however, the extension to, e.g. membrane proteins is straightforward. 
The understanding of the atomistic resolution structures of molecules in biologically relevant conditions 
significantly advances understanding about fundamental chemistry and also supports the development of, 
for example, new biomaterials or drug delivery systems.

@@

The usage of molecular dynamics simulations and open collaboration are adequate for the
problem at hand since the simulations are currently the most straightforward method to 
construct the atomistic resolution structure of molecules to interpret the NMR experiments. On the other hand,
enormous amount of simulation work was required for this work, and the only practical
solution to collect this data is the used open collaboration approach.
As result, we have produced original chemical insight for the atomistic resolution 
structures of phospholipids in various biologically relevant conditions.

>>>>

Please find attached to this message a manuscript that we would like to submit for publication 
in \textit{Journal of the american chemical society} (JACS): 
`Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions', 
by A. Botan et al. In the manuscript we combine extensive amount of experimental Nuclear Magnetic Resonance (NMR)
and molecular dynamics simulation data to understand the atomistic resolution structure of phospholipid molecules and their assemblies.

We believe that the manuscript is interesting for the wide and diverse contemporary audience of
JACS since the used combination of experiments and simulations is shown to be successfull in
resolving the atomistic resolution structure of biomolecules in various biologically relevant conditions.
The approach is demonstrated for lipids, however, the extension to, e.g. membrane proteins is straightforward. 
Such an atomistic resolution of  biomolecular structure
significantly advances the understanding in fundamental chemistry, molecular biology, and also supports the development of applications, 
for example new biomaterials or drug delivery systems.

@@

The usage of molecular dynamics simulations and open collaboration are adequate for the
problem at hand. Indeed, such simulations are currently the most straightforward method to 
construct atomistic resolution structures to interpret NMR experiments, but
enormous amount of simulation work was required for this work. The only practical
solution to collect this data is the open collaboration.
As result, we have produced original chemical insight for the atomistic resolution 
structures of phospholipids in various biologically relevant conditions.
